Golf-Sport: Managing Operations \\ A Case Study in Optimization

### 2018-04-24 Paper.tex
Rough Draft
Submitted to professor for 2 page eval
All sorts of stuff
added to paper, adjusted model for different runs

\author{John D. Bulger \& Matthew Hess, Valparaiso University}

@@

\subsection{Practicality Constraints}
Add in more practical minimums to develop a more realistic solution
\subsection{Range Sensitivity}
Conduct range sensitivity, examine extra problems in case study
\section{Conclusions \& Implications}
\subsection{Mathematical Approach}
Evaluate our approach, suggest changes in future.
\subsection{Company Approach}
Discuss optimized solution, range sensitivity, business suggestions
	\newpage
	\pagenumbering{gobble}
	\begin{thebibliography}{5}

>>>>

\author{John D. Bulger \& Matthew T. Hess, Valparaiso University}

@@

\section{Added Practicality Constraints}
Add in more practical minimums to develop a more realistic solution %needs finished
\section{Range Sensitivity}
Range sensitivity and resource increases were examined in regards to this problem.  The two main points of focus (as supplied by the case study) are a hypothetical increase in total maximum demand and proposed increases in advertising or graphite budget.  Both of these situations 
will be examined independently, using the initial mathematical model as the basis.
\subsection{Advertising Budget v. Graphite Supply}
The case study of the Golf-Sport problem presents a situation:  which would be more beneficial for the company, more monthly advertising budget or more graphite stock?  Since an amount of increase was not given, the situation was modeled with double the resources in the original problem.  
This allowed for a \$40,000 monthly advertising budget or a 2,000 pound monthly graphite stock.  As was the case before, advertising budget did not carry over to the next period, but graphite stock was assumed to.\par
These new parameters were incorporated separately into two different runs of the model.  Graphite was determined to be the more valuable resource, as it increases the maximum profit to \$968,831.  This profit potential is notably larger than the baseline of \$940,366 and the increased advertising 
profit of \$940,110.  This should help show Golf-Sport the importance of graphite to the operation, and perhaps motivate the company to obtain more graphite stock.
\subsection{Doubling the Demand}
The Golf-Sport case study also proposes an interesting change:  if max demand were to double, would the company be able to benenfit and maximize their profit while utilizing the current production system as originally described?  The model was adjusted to account for a hypoethetical doubling of maximum demand while maintaining all of the original constraints as set forth in the model.  
Using this modified model, an integer solution was found.  The objective value (maximum profit) is optimized at \$998,330.  This is approximately a \$48,000 greater profit than the original demands yielded.  This shows that the model does benefit from the increased demands.
\par
Here to discuss slack %discuss slack and see which constraints are maxed out
\section{Conclusions \& Implications}
\subsection{Mathematical Approach}
Evaluate our approach, suggest changes in future.
\subsection{Company Approach}
Discuss optimized solution, range sensitivity, business suggestions
	\newpage
	\pagenumbering{gobble}
	\begin{thebibliography}{5}
